\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
cleanup noise figures
donot use vtl, use L

(To be written by Nathan)

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection.png}
\caption{}
\label{fig:noisy_pad_before_rejection}
\end{figure}

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
\caption{}
\label{fig:noisy_pad_after_rejection}
\end{figure}

@@

For the energy deposit, $\frac{dE}{dx}$ is calculated in this way:
\begin{equation}
 \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{Gi}}{vtl}
\end{equation}
Where the sum runs over all the hits of the track and $G_{i}$ is the gain of 
the associated pad. The $vtl$ is the visible track length in the active drift 
volume.

>>>>

\begin{figure}[tb]\centering
\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection2.png}
\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection2.png}
\caption{The ADC vs. TDC spectrum for an example noisy channel before (top) and after (bottom) noise rejection algorithms.  Only hits associated with tracks are included, and the selection of events and tracks is the same in both plots.}
\label{fig:noise}
\end{figure}

%\begin{figure}[tb]
%\hspace{-0.4cm}
%\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
%\caption{}
%\label{fig:noisy_pad_after_rejection}
%\end{figure}

@@

For the energy deposit, $\frac{dE}{dx}$ is calculated in this way:
\begin{equation}
 \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{G_i}}{L}
\end{equation}
Where the sum runs over all the hits of the track, $G_{i}$ is the gain of 
the associated pad, and $L$ is the visible track length in the active drift 
volume.
